Figure 5 - IP-MS

### 2024-07-05 ms_figure_5_ipms.Rmd
Remove heatmaps from Figure 5 (now in Figure 2)

---
title: "Figure 4 - IP-MS"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds150: "data/ipms_150_sce.rds"
    rds500: "data/ipms_500_sce.rds"
    rdsdal2: "data/ipms_dal2_sce.rds"
    complexes: "data/complexes.json"
    baitclass: "data/ipms_bait_class.txt"
    dnabinders: "data/Gene_list_DNAbinders_proteincoding.txt"
    rnabinders: "data/Gene_list_RNAbinders_proteincoding.txt"
    idmap: "data/id_mapping_table.txt"
    dbdtxt: "data/TF_DBD_annotation.txt"
---

@@

mode(binary_mat) <- "character"
ht_opt(HEATMAP_LEGEND_PADDING = unit(0, "mm"))
hm1saga_nua4 <- Heatmap(
    binary_mat, 
    cluster_rows = FALSE, 
    cluster_columns = FALSE, 
    col = binary_heatmap_colors, 
    border = TRUE, 
    border_gp = gpar(lwd = 0.5),
    name = " ", 
    na_col = binary_heatmap_colors["FALSE"],
    column_names_gp = gpar(fontsize = ft),
    row_names_gp = gpar(fontsize = fl),
    show_row_names = TRUE, show_column_names = TRUE, 
    use_raster = FALSE, show_heatmap_legend = TRUE,
    right_annotation = rowAnnotation(
        df = binary_annot, 
        col = list(SAGA = c(`TRUE` = complex_colors[["SAGA"]],
                            `FALSE` = binary_heatmap_colors[["FALSE"]]),
                   NuA4 = c(`TRUE` = complex_colors[["NuA4"]],
                            `FALSE` = binary_heatmap_colors[["FALSE"]])),
        show_legend = FALSE),
    heatmap_height = unit(h_ipmsHm * 0.945, "mm"), # whole heatmap height
    column_title_gp = gpar(fontsize = ft),
    heatmap_legend_param = list(title_gp = gpar(fontsize = ft),
                                at = c("FALSE", "TRUE"),
                                labels = c("", "adj. p < 0.05 &\nlog2FC > 1"), 
                                legend_gap = unit(0, "mm"))
)

hm_150_saga_nua4 <- grid.grabExpr(
    hm1sn <- draw(hm1saga_nua4, merge_legend = TRUE,
                  heatmap_legend_side = "bottom",
                  annotation_legend_side = "right",
                  align_heatmap_legend = "global_center",
                  padding = unit(c(3, 1, 1, 1), "mm")),
    width = w_ipmsHm, height = h_ipmsHm
)

@@

```{r Fig4}
#| fig.width: 9.8
#| fig.height: 14.5

cowplot::plot_grid(
    hm_150,
    plot_grid(gg_retain1, NULL, hm_150_saga_nua4, nrow = 1, rel_widths = c(1, 0.05, 0.75)),
    hm_500,
    gg_retain2,
    nrow = 2,
    labels = c("A", "C", "B", "D"),
    align = "v",
    axis = "b"
)
```

@@

```{r suppFig4}
#| fig.width: 10.8
#| fig.height: 14.8
#| warning: false

cowplot::plot_grid(
    wrap_plots(ggpca1, ggpca2, ggatf1, ggpca3, hm_150_bait, hm_500_bait, ncol = 2) + 
        plot_annotation(tag_levels = list(c("A", "", "", "", "B"))) & 
        theme(plot.tag = element_text(size = 14, face = "bold")),
    cowplot::plot_grid(
        NULL,
        legend_bait_1, 
        legend_bait_2,
        NULL,
        nrow = 1,
        rel_widths = c(1, 2, 2, 1)
    ),
    ncol = 1,
    rel_heights = c(12, 1)
)
```

>>>>

---
title: "Figure 5 - IP-MS"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds150: "data/ipms_150_sce.rds"
    rds500: "data/ipms_500_sce.rds"
    rdsdal2: "data/ipms_dal2_sce.rds"
    complexes: "data/complexes.json"
    baitclass: "data/ipms_bait_class.txt"
    dnabinders: "data/Gene_list_DNAbinders_proteincoding.txt"
    rnabinders: "data/Gene_list_RNAbinders_proteincoding.txt"
    idmap: "data/id_mapping_table.txt"
    dbdtxt: "data/TF_DBD_annotation.txt"
---

@@

mode(binary_mat) <- "character"
ht_opt(HEATMAP_LEGEND_PADDING = unit(0, "mm"))
hm1saga_nua4 <- Heatmap(
    binary_mat, 
    cluster_rows = FALSE, 
    cluster_columns = FALSE, 
    col = binary_heatmap_colors, 
    border = TRUE, 
    border_gp = gpar(lwd = 0.5),
    name = " ", 
    na_col = binary_heatmap_colors["FALSE"],
    column_names_gp = gpar(fontsize = ft),
    row_names_gp = gpar(fontsize = fl),
    show_row_names = TRUE, show_column_names = TRUE, 
    use_raster = FALSE, show_heatmap_legend = TRUE,
    right_annotation = rowAnnotation(
        df = binary_annot, 
        col = list(SAGA = c(`TRUE` = complex_colors[["SAGA"]],
                            `FALSE` = binary_heatmap_colors[["FALSE"]]),
                   NuA4 = c(`TRUE` = complex_colors[["NuA4"]],
                            `FALSE` = binary_heatmap_colors[["FALSE"]])),
        show_legend = FALSE),
    heatmap_height = unit(1.125 * h_ipmsHm, "mm"), # whole heatmap height
    column_title_gp = gpar(fontsize = ft),
    heatmap_legend_param = list(title_gp = gpar(fontsize = ft),
                                at = c("FALSE", "TRUE"),
                                labels = c("", "adj. p < 0.05 &\nlog2FC > 1"), 
                                legend_gap = unit(0, "mm"))
)

hm_150_saga_nua4 <- grid.grabExpr(
    hm1sn <- draw(hm1saga_nua4, merge_legend = TRUE,
                  heatmap_legend_side = "bottom",
                  annotation_legend_side = "right",
                  align_heatmap_legend = "global_center",
                  padding = unit(c(3, 1, 1, 1), "mm")),
    width = w_ipmsHm, height = 1.125 * h_ipmsHm
)

@@

```{r Fig5}
#| fig.width: 9.8
#| fig.height: 14.5

cowplot::plot_grid(
    cowplot::plot_grid(
        plot_grid(gg_retain1, NULL, hm_150_saga_nua4, nrow = 1, rel_widths = c(1, 0.05, 0.75)),
        gg_retain2,
        hm_150_bait, hm_500_bait,
        rel_heights = c(7, 4),
        labels = c("A", "B", "C", "D")
    ),
    cowplot::plot_grid(
        NULL,
        legend_bait_1, 
        legend_bait_2,
        NULL,
        nrow = 1,
        rel_widths = c(1, 2, 2, 1)
    ),
    nrow = 2,
    rel_heights = c(12, 1)
)
```

@@

```{r suppFig5}
#| fig.width: 10.8
#| fig.height: 10.8
#| warning: false

wrap_plots(ggpca1, ggpca2, ggatf1, ggpca3, ncol = 2) + 
    # plot_annotation(tag_levels = list(c("A", "", "", "", "B"))) & 
    theme(plot.tag = element_text(size = 14, face = "bold"))
```
